%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemLink}[3]{
  \item\small{
   % \textbf{\href{#1}{#2}}{: #3 \vspace{-2pt}}
    \textbf{\href{#1}{\small #2}}{: #3 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Sarav Rajavelu}} & Email : \href{mailto:rajavelu.1@osu.edu}{rajavelu.1@osu.edu}\\
  \href{https://github.com/saravrajavelu}{github.com/saravrajavelu}  \textbullet\,  \href{https://www.linkedin.com/in/saravrajavelu/}{linkedin.com/in/saravrajavelu} & Mobile : +1-614-286-1199 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Ohio State University}{Columbus, OH}
      {Master of Science in Computer Science;  GPA: 4.0  /4.0}{Aug. 2017 --May. 2019}
    \resumeSubheading
      {Vellore Institute of Technology}{Vellore, India}
      {Bachelor of Technology in Computer Science and Engineering;  GPA: 8.23 /10.0}{Aug. 2011 -- May. 2015}
  \resumeSubHeadingListEnd

% Need to do this
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Python (scikit-learn, NumPy, SciPy, Pandas), R, SQL, SQL Server}
    \resumeSubItem{Technologies}{R Studio, SQL Server Integration Services, Informatica PowerCenter}
    \resumeSubItem{Coursework}{Artificial Intelligence, Data Mining, Social Media \& Text Analytics, Database Systems, Algorithms}
    \resumeSubItem{Technical}{Machine Learning (Classification, Regression, Feature Engineering), Deep Learning, Natural Language Processing, Data Visualization, Data Scraping}
    \resumeSubItem{Certifications}{R Programming – Statement of Accomplishment with Distinction, Coursera}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

%% Emplay Analytics 
    \resumeSubheading
      {Emplay Analytics}{Bangalore, India}
      {Analytics Consultant}{Jun. 2016 - Jun. 2017}
      \resumeItemListStart
	\item
          {Developed innovative data driven, action recommendations to help sales representatives predictably meet their sales
quota and improve sales in the B2B domain.}
        \item
{Solved business problems such as lead classification, forecasting the probability of a sales, performance forecasting of
sales teams and sales representative performance coaching using R.}
	\item
          {Designed algorithms using classification trees and regression models to provide prescriptive solutions.}
      \resumeItemListEnd



%% Deloitte Consulting
    \resumeSubheading
      {Deloitte Consulting}{Bangalore, India}
      {Business Technology Analyst}{Aug. 2015 - May. 2016}
      \resumeItemListStart
	\item
          {Developed interfaces for Data Processing, Data Conversion and Inbound and Outbound migration of Data using SQL,
SSIS, SQL Jobs and Batch Files for use through the CRM Software Application – Siebel.}
%        \item
%          {Worked on large scale migration of patient records and pharmaceutical data.}
	\item
          {Developed processes to detect inconsistencies in data, creating error logs and reporting them to the client.}
      \resumeItemListEnd

%% OhioState
    \resumeSubheading
      {The Ohio State University}{Columbus, OH}
      {Graduate Teaching Assistant}{Jan. 2018 - May. 2018}
      \resumeItemListStart
        \resumeItem{CSE 2111 Spreadsheets and Databases}
	{Lab Instructor for the undergraduate course that taught spreadsheet and database modeling, programming concepts and techniques to solve business related problems.}
	%https://cse.osu.edu/courses/modeling-and-problem-solving-spreadsheets-and-databases-2111.}
      \resumeItemListEnd
 \resumeSubHeadingListEnd



%-----------PROJECTS-----------------
\section{Projects}

	\resumeSubHeadingListStart

%% Sentiment in Football Tweets
		\projectSubheading
 		{Sentiment in Football Tweets}{Jun. 2016 - Jul. 2016}
			\resumeItemListStart
				\item
				{Developed an algorithm to track the sentiment in Tweets relating to a football game using NLP.}
%				\item
%				{The sentiment score at each minute of the game was calculated by aggregating all Tweets extracted at that minute, using a sentiment dictionary to assign a score to each Tweet.}
				\item
				{The calculated sentiment score at each minute was used to plot a ‘sentiment score versus game time’ graph to study the correlation between spikes in the graph with an event in the game.}
		      \resumeItemListEnd
 	
%% Feature Based Review Summarization
		\projectSubheading
 		{Feature Based Review Summarization}{ Dec. 2014 – Mar. 2015}
			\resumeItemListStart
				\item
				{Developed an algorithm to produce a feature-based scoring of a product using the customer feedback.}
%				\item
%				{Designed a web scraper to build a sentiment dictionary using a seed word and word-synonym based approach.}
%				\item
%				{The algorithm scores each individual feature of the product that is mentioned in the reviews on a scale of 0-5.}
		      \resumeItemListEnd

%%Exploratory Data Analysis \& Classification
		\projectSubheading
 		{Exploratory Data Analysis \& Classification }{}
			\resumeItemListStart
				\resumeItemLink{https://github.com/saravrajavelu/LogisticRegression}{Logistic Regression}
    				 {Built using NumPy to predict whether a student will be admitted to a unversity or not.}
				\resumeItemLink{https://github.com/saravrajavelu/TwitterLanguageMix}{Twitter Lang Mix}
    				 {Analysis of the spread of languages, emojis and comparison of \href{https://github.com/saffsd/langid.py}{LangID} vs Twitter's Lang ID.}
				\resumeItemLink{https://github.com/saravrajavelu/Adult-Income-Analysis}{Adult Income}
    				 {Analysis and comparison of classifiers like Neural Nets, SVM, Decision Trees and Adaboost.}
		      \resumeItemListEnd

	\resumeSubHeadingListEnd



%--------Awards------------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{High 5 Award for Exemplary Employee Performance}{Emplay Analytics, 3rd Quarter of 2016}
    \resumeSubItem{Applause Award for Outstanding Performance}{Deloitte Consulting, November 2015}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
